Modeling the Learning of the Russian Genitive Case

### 2023-12-10 paper/paper.tex
add the github
conclusion added

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\title{Instructions for ACL 2019 Proceedings}

@@

@@

\bibliography{paper}{}
\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review. Upon acceptance, the appendices come after the references, as shown here. Use
\verb|\appendix| before any appendix section to switch the section
numbering over to letters.

\end{document}

>>>>

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

@@

\title{Modeling the Learning of the Russian Genitive Case}

@@

  All code written for this paper, including X-SAMPA translation and model training,
  is available at \url{https://github.com/nickbclifford/genitive}.

@@

Although we were unable to adequately test our neural network hypotheses due to the
failure of our decoder network in converting the networks' outputs back to a phonological
representation, we have nonetheless shown that the networks are capable of learning the
genitive case's patterns to some extent with the Wickelphone/Wickelfeature schema described
in this paper. Further investigation of the intended implementation of the decoder network
could potentially demonstrate definitively whether or not the neural networks truly acquired 
the proper formation of the genitive case, and which of the two sets of networks more closely
models the acquisition of these cases in children with Russian as a native language.

Future work in this subject matter could use our design to model learning with the other cases 
of Russian, namely the dative, instrumental, and prepositional cases. It could also explore the
acquisition of the different forms of adjectives, which also decline for grammatical case and
number, or potentially the outcome of trying to learn both forms at once. All of these cases
tend to show greater degrees of regularity compared to the genitive case, meaning that a neural network
learning one or more of these cases is more likely to yield better results. This design
may not suit modeling of learning the Russian accusative case, however, because the endings used in the accusative depends on whether the noun is animate (i.e. a living being) or not.

\bibliography{paper}{}
\bibliographystyle{acl_natbib}
\end{document}
